---
title: "Table of Content"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
  html_notebook:
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: '3'
---

<style type="text/css">

body{ /* Normal  */
      font-size: 14px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
}
h1 { /* Header 1 */
  font-size: 18px;
  color: Black;
}
h2 { /* Header 2 */
    font-size: 16px;
  color: DarkBlue;
}
}
h3 { /* Header 3 */
    font-size: 14px;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>


```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
knitr::opts_chunk$set(fig.width=12, fig.height=11) 
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(plotly)
library(data.table)
library(ggplot2)
library(tidyverse)
library(tmap)
library(sf)
library(ggmap)
library(XML)
library(RCurl)
library(scrapeR)
library(lubridate) 
library(RColorBrewer)
library(odbc)
```


```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
# Connection to ARCHIVE_940
# connection <- dbConnect(odbc(),
                 #Driver = "SQL Server",
                 #Server = "vm-safetypad.bphcad.local",
                 #DataSource = "10.119.1.20",
                 #InitialCatalog = "ARCHIVE_940",
                 #Trusted_Connection="yes")
# Query to get CAD data
# sqlcm <- "SELECT DISTINCT a.num_1, a.prim_unit as unit_id, e.dispo, a.priority, a.tycod, a.ad_ts, a.ad_sec,a.ds_ts,a.ds_sec, (CAST(a.ar_sec AS decimal(18, 2)) - CAST(a.ad_sec AS decimal(18, 2))) / 60 AS resptime, (CAST(a.ds_sec AS decimal(18, 2))- CAST(a.ad_sec AS decimal(18, 2))) / 60 AS disptime, (CAST(a.en_sec AS decimal(18, 2)) - CAST(a.ds_sec AS decimal(18, 2))) / 60 AS enrtetime, (CAST(a.ar_sec AS decimal(18, 2)) - CAST(a.ds_sec AS decimal(18, 2))) / 60 AS travtime,(CAST(a.tr_sec AS decimal(18, 2)) - CAST(a.ar_sec AS decimal(18, 2))) / 60 AS onscenetime,(CAST(a.xsec AS decimal(18, 2)) - CAST(a.ta_sec AS decimal(18, 2))) / 60 AS athosptime,common_event.earea, common_event.zip, CONVERT(int, SUBSTRING(a.ad_ts, 5, 2)) AS month,a.reopen,CONVERT(DATE, LEFT(a.ad_ts, 8), 101) AS run_dt, DATEPART(wk, CONVERT(DATETIME, LEFT(a.ad_ts, 8), 101) + @@DATEFIRST) AS weeknum,a.sub_tycod,a.eid, COALESCE (ISNULL(common_event.estnum, '') + ' ' + common_event.efeanme + ' ' + ISNULL(common_event.efeatyp, ''), CASE WHEN xstreet1 IS NULL THEN common_event.ecompl ELSE xstreet1 + '/' + xstreet2 END, CASE WHEN common_event.ecompl IS NULL THEN common_event.loc_com ELSE NULL END) AS location,en_ts,en_sec,ar_ts,ta_ts,tr_ts,ar_sec,ta_sec,tr_sec,xsec,latitude,longitude FROM  [10.119.1.20].[ARCHIVE_940].[dbo].[common_event] INNER JOIN  [10.119.1.20].[ARCHIVE_940].[dbo].[agency_event] as a ON common_event.eid = a.eid LEFT OUTER JOIN [10.119.1.20].[ARCHIVE_940].[dbo].[ev_dispo] AS e INNER JOIN(SELECT num_1, MAX(row_num) AS row_num FROM [10.119.1.20].[ARCHIVE_940].[dbo].[ev_dispo] WHERE (num_1 LIKE 'E%') GROUP BY num_1) AS tb ON e.num_1 = tb.num_1 AND e.row_num = tb.row_num AND e.curent = 'T' ON e.num_1 = a.num_1 WHERE CONVERT(DATE, LEFT(a.ad_ts, 8), 101) <= '11/27/2020' and CONVERT(DATE, LEFT(a.ad_ts, 8), 101) <= '11/27/2020' AND (e.dispo NOT LIKE 'DUP%' or e.dispo is null) AND (a.priority in (1,2,3) Or(a.priority = 4 AND a.ds_ts IS NOT NULL) or (a.priority in (5,7,9,0) and e.dispo='TRN')) and a.ag_id='BEMS' ORDER BY a.num_1"
# CAD <- dbGetQuery(connection, sqlcm)
# print(CAD)

# Import CAD data manually
CAD <- read.csv("~/Desktop/CAD.Data2.csv", sep = ",", header = FALSE,
stringsAsFactors=FALSE)
colnames(CAD) <- c("num_1","unit_id","dispo","priority","tycod","ad_ts","ad_sec","ds_ts","ds_sec","resptime","disptime","enrtetime","travtime","onscenetime","athosptime","earea","zip","month","reopen","run_dt","weeknum","sub_tycod","eid","location","en_ts","en_sec","ar_ts","ta_ts","tr_ts","ar_sec","ta_sec","tr_sec","xsec","latitude","longitude")
# Make Date
CAD$run_dt <- as.Date(CAD$run_dt,format="%Y-%m-%d")
# Consider specific Date
MyDate <- "2020-11-27"
previous.week <- as.Date(MyDate)-6
cad.weekly <- subset(CAD, CAD$run_dt >= as.Date(previous.week) &
               CAD$run_dt <= as.Date(MyDate))

# Connect to SafetyPad System
search_url <- paste0("https://bostonems.safetypad.com/api/?action=search_pcrs&columns=eCase.01m,eResponse.03,eDispatch.01,eTimes.03,eScene.17,eResponse.02,eResponse.14,eResponse.14s,eResponse.15,eDisposition.12,eDisposition.01&api_key=PxTwmC6_XjwMQEhEKTOGO8Uf6_dosfpy9cwXvIBwyYs", Sys.getenv("PxTwmC6_XjwMQEhEKTOGO8Uf6_dosfpy9cwXvIBwyYs"))
search <- httr::GET(search_url)
doc.search <- xmlParse(search, useInternalNodes = TRUE)
a1 <- setNames(xmlToDataFrame(node=getNodeSet(doc.search, "//pcr/eCase.01m")), "eCase.01m")
a2 <- setNames(xmlToDataFrame(node=getNodeSet(doc.search, "//pcr/eResponse.03")), "eResponse.03")
a3 <- setNames(xmlToDataFrame(node=getNodeSet(doc.search, "//pcr/eDispatch.01")), "eDispatch.01")
a4 <- setNames(xmlToDataFrame(node=getNodeSet(doc.search, "//pcr/eTimes.03")), "eTimes.03")
a6 <- setNames(xmlToDataFrame(node=getNodeSet(doc.search, "//pcr/eScene.17")), "eScene.17")
a9 <- setNames(xmlToDataFrame(node=getNodeSet(doc.search, "//pcr/eResponse.02")), "eResponse.02")
a10 <- setNames(xmlToDataFrame(node=getNodeSet(doc.search, "//pcr/eResponse.14")), "eResponse.14")
a11 <- setNames(xmlToDataFrame(node=getNodeSet(doc.search, "//pcr/eResponse.14s")), "eResponse.14s")
a12 <- setNames(xmlToDataFrame(node=getNodeSet(doc.search, "//pcr/eResponse.15")), "eResponse.15")
a13 <- setNames(xmlToDataFrame(node=getNodeSet(doc.search, "//pcr/eDisposition.12")), "eDisposition.12")
a14 <- setNames(xmlToDataFrame(node=getNodeSet(doc.search, "//pcr/eDisposition.01")), "eDisposition.01")
pcr_weekly <- cbind(a1,a2,a3,a4,a6,a9,a10,a11,a12,a13,a14)

m <- as.POSIXct(pcr_weekly$eTimes.03,format="%Y-%m-%d %H:%M:%S",tz=Sys.timezone())
h <- ymd_hms(pcr_weekly$eTimes.03,tz=Sys.timezone())
pcr_weekly$eTimes.03 <- as.Date(h, format = "%Y-%m-%d %H:%M:%S'")
pcr_weekly <- subset(pcr_weekly, pcr_weekly$eTimes.03 >= as.Date(previous.week) &
               pcr_weekly$eTimes.03 <= as.Date(MyDate))

# Merging CAD data and PCR data
cad.weekly$num_1 <- gsub("E*", "", cad.weekly$num_1)
cad.pcr <- merge(cad.weekly, pcr_weekly, by.x = "num_1", by.y = "eResponse.03")
```



\


# Results For a Week From `r previous.week` to `r MyDate`
\

\

## Number of Incidents by Shift For a Week From `r previous.week` to `r MyDate` 
\

```{r, echo=FALSE, warning=FALSE, message=FALSE, comment=""}
shift <- as.data.frame(table(cad.pcr$eResponse.14s))
ggplot(shift, aes(Var1, Freq, fill = as.factor(shift$Var1))) + geom_bar(stat = 'identity') + theme_bw()+ ggtitle("Number of Incidents by shift") + xlab("Shift") + labs(fill="Shift") +
  scale_fill_manual(values=c("lightblue", "deepskyblue3", "blue3")) + geom_text(aes(label = Freq), vjust = -0.6, size = 3)  + theme(text = element_text(size=14)) + ylab("Frequency") 


```



\


## Call History by Disposition For a Week From `r previous.week` to `r MyDate`
\

```{r, echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cad.pcr$eDisposition.12 <- ifelse(cad.pcr$eDisposition.12 == "" | cad.pcr$eDisposition.12 == "Canceled (Prior to Arrival At Scene)" | cad.pcr$eDisposition.12 == "No Patient Found (Canceled on Scene)" | cad.pcr$eDisposition.12 == "Treated, Transferred to Other EMS"| cad.pcr$eDisposition.12 == "No Patient Contact (Canceled on Scene)" , NA, ifelse(cad.pcr$eDisposition.12 == "Dead at Scene - No Resus - Not Transported"| cad.pcr$eDisposition.12 == "Dead at Scene - Resus Attempted - No Transport", "Referred to the Medical Examiner", as.character(cad.pcr$eDisposition.12)))

num_disposition <- as.data.frame(table(cad.pcr$eDisposition.12))

ggplot(num_disposition, aes(x = Var1, Freq)) + geom_bar(stat = 'identity', fill="cornflowerblue") + theme_bw()+
  theme(axis.text.x = element_text(angle=90, vjust=0.6, size = 14)) + ggtitle("Call History by Disposition") + xlab("Disposition") + geom_text(aes(label = Freq), vjust = -0.4, size = 3) + theme(text = element_text(size=14))+ ylab("Frequency")
```



```{r, echo=FALSE, warning=FALSE, message=FALSE, comment="", results='hide'}
cad.pcr$eScene.17 <- ifelse(cad.pcr$eScene.17 == "Boston" |  cad.pcr$eScene.17 == "boston", "BOSTON", as.character(cad.pcr$eScene.17)) 
cad.pcr$eScene.17 <- ifelse(cad.pcr$eScene.17 == "Dorchester", "DORCHESTER", ifelse(cad.pcr$eScene.17 == "SOUTH BOSTON"| cad.pcr$eScene.17 == "South Boston" | cad.pcr$eScene.17 == "DORCHESTER" & cad.pcr$zip == "02127", "South Boston", ifelse(cad.pcr$eScene.17 == 'Roslindale' | cad.pcr$eScene.17 == "ROSLINDALE", "Roslindale", as.character(cad.pcr$eScene.17)))) 

cad.pcr$eScene.17 <- ifelse(cad.pcr$eScene.17 == "DORCHESTER" & cad.pcr$zip == "02121" | cad.pcr$zip == "02125", "Dorchester (ZIPs 02121, 02125)", ifelse(cad.pcr$eScene.17 == "DORCHESTER" & cad.pcr$zip == "02122" | cad.pcr$zip == "02124", "Dorchester (ZIPs 02122, 02124)", ifelse(cad.pcr$eScene.17 == "BOSTON" & cad.pcr$zip == "02115", "Fenway", ifelse(cad.pcr$eScene.17 == "JAMAICA PLAIN" |  cad.pcr$eScene.17 == "Jamaica Plain", "Jamaica Plain", ifelse(cad.pcr$eScene.17 == "BOSTON" & cad.pcr$zip == "02111" | cad.pcr$zip == "02118", "South End", ifelse(cad.pcr$eScene.17 == "BOSTON", "Back Bay, Beacon Hill, Downtown, North End, West End", ifelse(cad.pcr$eScene.17 == "BRIGHTON"| cad.pcr$eScene.17 == "Brighton","Allston/Brighton", ifelse(cad.pcr$eScene.17 == "EAST BOSTON", "East Boston", ifelse(cad.pcr$eScene.17 == "HYDE PARK", "Hyde Park", ifelse(cad.pcr$eScene.17 == "MATTAPAN"| cad.pcr$eScene.17 == "mattapan" | cad.pcr$eScene.17 == "DORCHESTER" & cad.pcr$zip == "02126", "Mattapan", ifelse(cad.pcr$eScene.17 == "ROXBURY" | cad.pcr$eScene.17 == "DORCHESTER" & cad.pcr$zip == "02119", "Roxbury", ifelse(cad.pcr$eScene.17 == "WEST ROXBURY", "West Roxbury", ifelse(cad.pcr$eScene.17 == "", NA, as.character(cad.pcr$eScene.17))))))))))))))

```




\


## Number of Incidents by Shift Across Neighborhoods For a Week From `r previous.week` to `r MyDate`
\


```{r, echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cad <- cad.pcr[!is.na(cad.pcr$eScene.17),]
ggplot(cad) + geom_bar(aes(eScene.17, fill=as.factor(cad$eResponse.14s))) + theme_bw() + ggtitle("Number of incidents for each neighborhood by shift") + xlab("Neighborhoods and shift") + theme(axis.text.x = element_text(angle=90, vjust=0.6, size = 12)) + labs(fill = "shift") + scale_fill_manual(values=c("lightblue", "deepskyblue3", "blue3")) + theme(text = element_text(size=14))

```


\


## Number of Incidents Across Neighborhoods For a Week From `r previous.week` to `r MyDate`
\




```{r, echo=FALSE, warning=FALSE, message=FALSE, comment=""}


df.nbhd <- as.data.frame(table(cad.pcr$eScene.17)) %>% 
  arrange(desc(Freq))

ggplot(df.nbhd, aes(x = reorder(Var1,Freq), y = Freq)) + geom_bar(stat = 'identity', fill="blue3") + theme_bw() + ggtitle("Number of incidents for each neighborhood") + xlab("Neighborhoods") + coord_flip() + geom_text(
    aes(label = Freq), 
    hjust = -0.4, size = 3,
    position = position_dodge(width = 1),
    inherit.aes = TRUE) + 
  coord_flip() + 
  theme_bw() + ylab("Frequency") + theme(text = element_text(size=12))
    
```



\

## Number of Incidents by Hospitals For a Week From `r previous.week` to `r MyDate`
\


\

```{r echo=FALSE, warning=FALSE, message=FALSE}
cad.pcr$eDisposition.01 <- ifelse(cad.pcr$eDisposition.01 == "", NA, as.character(cad.pcr$eDisposition.01))


hospital <- as.data.frame(table(cad.pcr$eDisposition.01)) %>% 
  arrange(desc(Freq))

ggplot(hospital, aes(reorder(Var1,Freq), y = Freq)) + geom_bar(stat = 'identity', fill="lightskyblue") + theme_bw() + ggtitle("Number of incidents by hospitals") + xlab("Hospitals") +
  theme(axis.text.x = element_text(angle=90, vjust=0.5, size = 14)) +  geom_text(
    aes(label = Freq), 
    hjust = -0.4, size = 3,
    position = position_dodge(width = 1),
    inherit.aes = TRUE) + 
  coord_flip() + 
  theme_bw() + ylab("Frequency") + theme(text = element_text(size=14))
```

\

\



```{r, echo=FALSE, warning=FALSE, message=FALSE, comment="", results='hide'}
cad.pcr$eDisposition.12 <- ifelse(cad.pcr$eDisposition.12 == 'Assist, Unit', 1, ifelse(cad.pcr$eDisposition.12 == "Exposure", 2, ifelse(cad.pcr$eDisposition.12 == "Referred to the Medical Examiner", 3, ifelse(cad.pcr$eDisposition.12 == "Party denies need (PDN)",4, ifelse(cad.pcr$eDisposition.12 == "Treated, Transported by EMS", 5, ifelse(cad.pcr$eDisposition.12 == "Patient Refusal",6, NA))))))

cad.pcr <- cad.pcr %>% rename(eScene = eScene.17,
                              eDisposition12 = eDisposition.12)
library(sqldf)
Categories <- sqldf("select eScene,
            sum(eDisposition12 == 1) as AssistUnit,
            sum(eDisposition12 == 2) as Exposure,
            sum(eDisposition12 == 3) as Referred_Medical_Examiner,
            sum(eDisposition12 == 4) as PartyDeniesNeed,
            sum(eDisposition12 == 5) as Treated_Transported_by_EMS,
            sum(eDisposition12 == 6) as PatientRefusal
            from 'cad.pcr'
            group by eScene")



names(Categories)[1] <- 'Neighborhoods'
Categories <- Categories[-1,]
```





\


## Disposition Based on Neighborhoods For a Week From `r previous.week` to `r MyDate`
\


```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide', comment=""}
nbhd <- st_read(dsn="~/Desktop/NHzip_2020-10-16/NHzip_2020-10-16.shp")
nbhd <- st_transform(nbhd, "+proj=longlat +datum=NAD83 +no_defs")
```

\


\



```{r, echo=FALSE, warning=FALSE, message=FALSE, comment=""}

nbhd <- merge(nbhd, Categories, by.x='Neighborho', by.y ="Neighborhoods", all.x =TRUE) 

pal <- brewer.pal(5,"YlOrBr")
pal <- c("#F5F5F5",pal)

tmap_mode('view')
map1 <- tm_shape(nbhd) + tm_polygons('AssistUnit' ,style="pretty", palette=pal, title = "Assist Unit") +tm_basemap(server = c('OpenStreetMap'))  + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) 

tmap_mode('view')
map2 <- tm_shape(nbhd) + tm_polygons('Exposure' ,style="pretty", palette=pal) +tm_basemap(server = c('OpenStreetMap'))  + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tmap_options(limits = c(facets.view = 6))

tmap_mode('view')
map3 <- tm_shape(nbhd) + tm_polygons('Referred_Medical_Examiner', style="pretty", palette=pal, title = "Referred Medical <br> Examiner") +tm_basemap(server = c('OpenStreetMap'))  + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) 

tmap_mode('view')
map4 <- tm_shape(nbhd) + tm_polygons('PartyDeniesNeed', style="pretty", palette=pal, title= "Party Denies Need") +tm_basemap(server = c('OpenStreetMap'))  + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) 


tmap_mode('view')
map5 <- tm_shape(nbhd) + tm_polygons('Treated_Transported_by_EMS',style="pretty", palette="YlOrBr", title = "Treated Transported <br> by EMS") +tm_basemap(server = c('OpenStreetMap'))  + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) 

tmap_mode('view')
map6 <- tm_shape(nbhd) + tm_polygons('PatientRefusal' ,style="pretty", palette="YlOrBr", title="Patient Refusal") +tm_basemap(server = c('OpenStreetMap'))  + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) 

tmap_arrange(map1, map2, map3, map4, map5, map6)

```

\
\

\


## Boston EMS Responses For a Week From `r previous.week` to `r MyDate`
\



```{r, echo=FALSE, warning=FALSE, message=FALSE, comment=""}
response <- as.data.frame(table(cad.pcr$eResponse.15))
names(response)[1] <- "EMS.Responses"
names(response)[2] <- "Count"
library(stargazer)
stargazer(response, summary=F, title="Boston EMS Responses", align=T, digits=4, type = "text", no.space=T, flip=F)
```

\


```{r, echo=FALSE, warning=FALSE, message=FALSE, comment=""}
cad.pcr <- cad.pcr %>% rename(eResponse15LevelofCare = eResponse.15)

cad.pcr$eResponse15LevelofCare <- ifelse(cad.pcr$eResponse15LevelofCare == 'ALS-Paramedic', 1, ifelse(cad.pcr$eResponse15LevelofCare == "BLS-AEMT", 2, ifelse(cad.pcr$eResponse15LevelofCare == "BLS-Basic /EMT", 3, NA)))

library(sqldf)
Categories2 <- sqldf("select eScene,
            sum(eResponse15LevelofCare == 1) as ALS_,
            sum(eResponse15LevelofCare == 2) as BLSA_,
            sum(eResponse15LevelofCare == 3) as BLS_
            from 'cad.pcr'
            group by eScene")

names(Categories2)[1] <- 'Neighborhoods'
Categories2 <- Categories2[-1,]
```


\

\


## Boston EMS Responses Based on Neighborhoods For a Week From `r previous.week` to `r MyDate` \
\

\

```{r, echo=FALSE, warning=FALSE, message=FALSE, comment=""}

nbhd2 <- merge(nbhd, Categories2, by.x='Neighborho', by.y ="Neighborhoods", all.x =TRUE) 
pal <- brewer.pal(5,"YlOrBr")
pal <- c("#F5F5F5",pal)

tmap_mode('view')
tm_shape(nbhd2) + tm_polygons(c('ALS_','BLSA_','BLS_') , style="pretty", palette = list("YlOrBr", pal, "YlOrBr"), title = c("ALS Paramedic", "BLS AEMT", "BLS Basic / EMT"))+tm_basemap(server = c('OpenStreetMap'))  + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) +
   tm_facets(nrow=1,ncol=3)  

```
\

\


## Priority Across Neighborhoods For a Week From `r previous.week` to `r MyDate` (According to CAD data)
\



```{r, echo=FALSE, warning=FALSE, message=FALSE, comment=""}
priority.df <- as.data.frame(table(cad.pcr$priority))
names(priority.df)[1] <- "Priority"
names(priority.df)[2] <- "Count"
library(stargazer)
stargazer(priority.df[-4,], summary=F, title="Priority", align=T, digits=4, type = "text", no.space=T, flip=F)
```
\


## Priority Across Neighborhoods For a Week From `r previous.week` to `r MyDate`
\


```{r, echo=FALSE, warning=FALSE, message=FALSE, comment=""}
library(sqldf)

Categories3 <- sqldf("select eScene,
            sum(priority == 1) as One,
            sum(priority== 2) as Two,
            sum(priority == 3) as Three
            from 'cad.pcr'
            group by eScene")

names(Categories3)[1] <- 'Neighborhoods'
Categories3 <- Categories3[-1,]
```

\

\

```{r, echo=FALSE, warning=FALSE, message=FALSE, comment=""}

nbhd3 <- merge(nbhd, Categories3, by.x='Neighborho', by.y ="Neighborhoods", all.x =TRUE) 

tmap_mode('view')
tm_shape(nbhd3) + tm_polygons(c('One', 'Two', 'Three'), style="pretty", palette = list("YlOrBr","YlOrBr", "YlOrBr")) +tm_basemap(server = c('OpenStreetMap'))  + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) + tm_facets(nrow=2,ncol=2)  

```

 






